State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some edition in the appendix
added the range of i in the URTSS algorithm for clarity
edidtion to frequency respnse analysis

@@

			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) 

@@

			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) 

@@

\begin{figure*}
	\label{fig:FreqAnalysis} 
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{Frequency analysis of the. \textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project. The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics. The dashed line shows the cut-off frequency (-3 dB point). \textbf{b} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.} 
\end{figure*}
Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum. \mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}

@@

The finite state space model given in \ref{eq:ReducedForm} is linear with respect to parameters. Therefore a least square (LS) method can be applied to estimate the unknown parameters. To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix

>>>>

\begin{equation}\label{eq:finalformstatespacemodel}

@@

			\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L

@@

			\mathcal X_{i,t+1}^{b-}=Q(\mathcal X_{i,t}^b) \quad i=0, \dots, 2L

@@

\begin{figure*}
	\label{fig:FreqAnalysis} 
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{Frequency analysis of the. \textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project. The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics. The dashed line shows the cut-off frequency (-3 dB point). \textbf{b} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.} 
\end{figure*}
Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum. \mike{Analysis said 1 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}\parham{maybe we can argue that this width is for perfect recunstruction up to 0.19 Hz which requires the smaller distance between basis functions and hence more number of basis functions but we choose to go for lower number of basis function and loosing high frequency contents.}

@@

The finite state space model given in \ref{eq:finalformstatespacemodel} is linear with respect to parameters. Therefore a least square (LS) method can be applied to estimate the unknown parameters. To create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix
